---
title: "R Notebook"
output: html_notebook
---

```{r, include=FALSE}
library(caret)
library(ROCR)
library(pROC)
library(MASS)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(ggfortify)
library(glmnet)
library(tidyverse)
```

# Homework

## Lasso

$$Lasso Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p|w_j|$$
2. Create and train model 
```{r}
train_size <- floor(0.75 * nrow(airquality))
set.seed(543)
train_pos <- sample(seq_len(nrow(airquality)), size = train_size)
train_regression <- airquality[train_pos,-c(1,2)]
test_regression <- airquality[-train_pos,-c(1,2)]

dim(train_regression)
dim(test_regression)
```

```{r}
ctrl =  trainControl(method = "boot", 15)

Lasso_regression <- train(Temp ~ Wind + Month, data = train_regression,
                          method = 'lasso', trControl= ctrl) 
```

Examine the residuals 
```{r}
lasso_test_pred <- predict(Lasso_regression, newdata = test_regression)

#plot the predicted values vs the observed values
plot_lasso_test_pred <- data.frame(Temp_test_pred = lasso_test_pred, 
                                   Observed_Temp = test_regression$Temp)
ggplot(data = plot_lasso_test_pred) +
  geom_point(aes(x=Observed_Temp, y = Temp_test_pred)) + 
  ggtitle("True Temp Value vs Predicted Temp Value Lasso Regression") +
  theme_bw()

#median residual value should be close to zero
median(resid(Lasso_regression))
```

#Homework:

1. Use the Breast Cancer dataset from the mlbench package, and predict whether the cancer is malignant or benign using one of the algorithms we learned about in class. Give some rationale as to why you chose this algorithm. Plot ROC curves, and confusion matrices. If you are choosing a hyperparameter like K or lambda, explain how and why you chose it. 

```{r}
#library
library(mlbench)
data(BreastCancer)
BreastCancer <-na.omit(BreastCancer)
#split into training and test set 
train_size <- floor(0.75 * nrow(BreastCancer))
set.seed(543)
train_pos <- sample(seq_len(nrow(BreastCancer)), size = train_size)
train_classifier <- BreastCancer[train_pos,]
test_classifier <- BreastCancer[-train_pos,]
dim(train_classifier)
dim(test_classifier)
```

I am using logistic regression because there are only two classes(malignant or benign) and linear regression is pretty good for this situation
```{r}
#train
train_classifier$Class <- factor(train_classifier$Class)
test_classifier$Class <- factor(test_classifier$Class)

ctrl <- trainControl(method = "repeatedcv", repeats = 15,classProbs = T,
                     savePredictions = T)

```

```{r, warning=FALSE}
#create model. logistic regression is a bionomial general linear model. 
logistic_regression <- train(Class ~ Cl.thickness + Cell.size + Cell.shape +
                               Marg.adhesion + Epith.c.size + Bare.nuclei + 
                               Bl.cromatin + Normal.nucleoli + Mitoses, 
                             data = train_classifier, 
                             method = "glm", family= "binomial",trControl = ctrl)
```

```{r}
#test
#predict class using x
logistic_regression_predict_class <- predict(logistic_regression, 
                                             newdata = test_classifier)

#confusion matrix
confusionMatrix(logistic_regression_predict_class, 
                reference = test_classifier$Class)

```

```{r}
# plot ROC
plot(x = roc(predictor = logistic_regression$pred$benign,
             response = logistic_regression$pred$obs)$specificities, 
     y = roc(predictor = logistic_regression$pred$benign, 
             response = logistic_regression$pred$obs)$sensitivities,
     col= "blue", xlim = c(1, 0), type ="l", ylab = "Sensitivity",
     xlab = "Specificity")
legend("bottomright", legend = paste("benign v versicolor --", 
                                     roc(predictor = logistic_regression$pred$benign,
                                         response = logistic_regression$pred$obs)$auc
, sep = ""), col = c("blue"), fill = c("blue"))
```